\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-29 paper/ms.tex
The accretion need not be recent (JMB)

% ------------------------
% nature summary paragraph
% ------------------------
% - a fully referenced paragraph, ideally of about 200 words, but certainly no
%   more than 300 words, aimed at readers in other disciplines.
% - This paragraph starts with a 2-3 sentence basic introduction to the field;
%   followed by a one-sentence statement of the main conclusions starting 'Here
%   we show' or equivalent phrase; and finally, 2-3 sentences putting the main
%   findings into general context so it is clear how the results described in
%   the paper have moved the field forwards.
% - annotated example: https://www.nature.com/nature/authors/gta/2c_Summary_para.pdf
% ------------------------
\section{Summary}
{\bf \noindent
  Stars that are born together are expected to have the same chemical
  compositions initially.
  Detailed chemical abundance studies of stars in wide binaries indeed reveal
  little to no abundance differences in most
  cases\citep{Gratton:2001aa,Desidera:2004aa}.
  However, the formation and evolution of different planetary systems around
  each star in a wide binary may eventually lead to differences in the chemical
  abundances of the component stars' radiative and convective
  layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
  Wide binary systems of two twin-like stars are particularly useful since such
  chemical signature may be more easily detectable as abundance differences,
  free from dependences on stellar parameters or confusion with Galactic
  chemical evolution.
  A handful of wide binaries that show small differences ($0.03$--$0.1$~dex)
  in their surface chemical abundances have been reported so far
  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,
    Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa},
  however, a conclusive example of planetary accretion has not yet been found.
  %
  Here we report the discovery of a comoving pair of bright, sun-like
  stars---HD~240430 and HD~240429, hereafter ``\bizarreone'' and
  ``\sunanalog''--- with significant differences ($\approx 0.2$~dex) in their
  chemical abundances that strongly suggest accretion of a massive rocky
  planetary system in one of the stars within the last billion years.
  The more metal-rich of the two, \bizarreone, shows an enhancement of refractory
  elements by $\approx 0.2$~dex and a small enhancement ($\lesssim 0.11$~dex) of
  (moderately) volatile elements.
  The two stars also show high \elem{Li} abundance given their age of $\sim 4$ Gyr,
  as inferred from their stellar parameters.
  We suggest that the star \bizarreone\ recently accreted
  $\approx 15$~\mearth\ of rocky material, selectively enhancing the
  refractory elements in its surface and convective envelope.
  The other star, \sunanalog, may also have had a similar accretion
  event given its high surface \elem{Li} abundance but of much smaller amount
  ($\approx 4$~\mearth).
  This pair of stars provides evidence that dynamical accretion of rocky planets
  does happen during the main-sequence lifetime of sun-like stars.
}

@@

The accretion scenario can naturally explain the anomalously high
surface \elem{Li} abundance in \bizarreone.
Because \elem{Li} is strongly depleted in old sun-like stars, yet
present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
late-time accretion of rocky planetary material will significantly
replenish the lithium in the star's surface.
For the present-day Sun, the accretion of $15~\mearth$ of bulk Earth-like
material would result in $\Delta\elemH{Li} \approx 1.6$~dex
(see inset of \figname~\ref{fig:deltaxh_tcrank}).
Incidentally, the \bizarreone-\sunanalog\ system has an age (informed by
stellar parameters) very close to the Sun ($\sim 4$~Gyr).
Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
to be ordinary, the accretion of $15$~\mearth\ by \bizarreone\ is consistent with a $1.65$~dex
enhancement in \elem{Li} abundance.
This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep.)
approximately $1.7$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
Furthermore, this implies that the accretion event should have happened
recently within the \elem{Li} depletion time ($\lesssim 1$~Gyr).
Finally, while the current analysis of \elem{Li} line assumed a solar ratio of
$^{6}\elem{Li}/^{7}\elem{Li}$ given the data, we predict that a higher resolution
spectrum of the star will reveal a significant $^{6}\elem{Li}$ which are
normally destroyed early in solar-type stars, but present in rocky
planets\cite{Israelian:2001}.

>>>>

% ------------------------
% nature summary paragraph
% ------------------------
% - a fully referenced paragraph, ideally of about 200 words, but certainly no
%   more than 300 words, aimed at readers in other disciplines.
% - This paragraph starts with a 2-3 sentence basic introduction to the field;
%   followed by a one-sentence statement of the main conclusions starting 'Here
%   we show' or equivalent phrase; and finally, 2-3 sentences putting the main
%   findings into general context so it is clear how the results described in
%   the paper have moved the field forwards.
% - annotated example: https://www.nature.com/nature/authors/gta/2c_Summary_para.pdf
% ------------------------
\section{Summary}
{\bf \noindent
  Stars that are born together are expected to have the same chemical
  compositions initially.
  Detailed chemical abundance studies of stars in wide binaries indeed reveal
  little to no abundance differences in most
  cases\citep{Gratton:2001aa,Desidera:2004aa}.
  However, the formation and evolution of different planetary systems around
  each star in a wide binary may eventually lead to differences in the chemical
  abundances of the component stars' radiative and convective
  layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
  Wide binary systems of two twin-like stars are particularly useful since such
  chemical signature may be more easily detectable as abundance differences,
  free from dependences on stellar parameters or confusion with Galactic
  chemical evolution.
  A handful of wide binaries that show small differences ($0.03$--$0.1$~dex)
  in their surface chemical abundances have been reported so far
  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,
    Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa},
  however, a conclusive example of planetary accretion has not yet been found.
  %
  Here we report the discovery of a comoving pair of bright, sun-like
  stars---HD~240430 and HD~240429, hereafter ``\bizarreone'' and
  ``\sunanalog''--- with significant differences ($\approx 0.2$~dex) in their
  chemical abundances that strongly suggest accretion of a massive rocky
  planetary system in one of the stars within the last billion years.
  The more metal-rich of the two, \bizarreone, shows an enhancement of refractory
  elements by $\approx 0.2$~dex and a small enhancement ($\lesssim 0.11$~dex) of
  (moderately) volatile elements.
  The two stars also show high \elem{Li} abundance given their age of $\sim 4$ Gyr,
  as inferred from their stellar parameters.
  We suggest that the star \bizarreone\ accreted
  $\approx 15$~\mearth\ of rocky material, selectively enhancing the
  refractory elements in its surface and convective envelope.
  The other star, \sunanalog, may also have had a similar accretion
  event given its high surface \elem{Li} abundance but of much smaller amount
  ($\approx 4$~\mearth).
  This pair of stars provides evidence that dynamical accretion of rocky planets
  does happen during the main-sequence lifetime of sun-like stars.
}

@@

The accretion scenario can naturally explain the anomalously high
surface \elem{Li} abundance in \bizarreone.
Because \elem{Li} is strongly depleted in old sun-like stars, yet
present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
late-time accretion of rocky planetary material will significantly
replenish the lithium in the star's surface.
For the present-day Sun, the accretion of $15~\mearth$ of bulk Earth-like
material would result in $\Delta\elemH{Li} \approx 1.6$~dex
(see inset of \figname~\ref{fig:deltaxh_tcrank}).
Incidentally, the \bizarreone-\sunanalog\ system has an age (informed by
stellar parameters) very close to the Sun ($\sim 4$~Gyr).
Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
to be ordinary, the accretion of $15$~\mearth\ by \bizarreone\ is consistent with a $1.65$~dex
enhancement in \elem{Li} abundance.
This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep.)
approximately $1.7$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
While the current analysis of \elem{Li} line assumed a solar ratio of
$^{6}\elem{Li}/^{7}\elem{Li}$ given the data, we predict that a higher resolution
spectrum of the star will reveal a significant $^{6}\elem{Li}$ which are
normally destroyed early in solar-type stars, but present in rocky
planets\cite{Israelian:2001}.
